Discrete Ordinates

### 2017-06-01 docprep/norris_phd_dissertation.tex
Added the rotating package for sideways tables
Added a not about future plans
Worked on the Vita

 % -*- mode: LaTeX -*-
 % ... preamble ...
\documentclass[times,12pt,titlepage]{mstthesis}
\doublespacing
\usepackage{threeparttable}
\usepackage[final]{graphicx}
\usepackage{psfrag}
\usepackage{listings}
\usepackage{minted}
\usepackage[noprefix]{nomencl}
\usepackage{subcaption}
\usepackage{xr}
\makenomenclature
\renewcommand{\nomgroup}[1]{
   \ifthenelse{\equal{#1}{A}}{\medskip \item \textbf{Roman}}{}%
   \ifthenelse{\equal{#1}{G}}{\medskip \item \textbf{Greek}}{}%
   \ifthenelse{\equal{#1}{S}}{\medskip \item \textbf{Subscripts}}{}%
}
\usepackage[nopar]{lipsum} % ... provides dummy text ...

@@

\begin{Vita}
Edward Norris graduated from Missouri University of Science and Technology in 2013 with a B.S. in both nuclear engineering and computer science, he went on to pursue a M.S. in computer science and a PhD in nuclear engineering.

His PhD work was funded by a fellowship through the NRC.

Previously he has participated in four summer internships with Sandia National Laboratories. While there, he served in various capacities ranging from cyber defense to radiation detection and neutron scatter simulation.

Edward was awarded SOME AWARDS.

@@

>>>>

 % -*- mode: LaTeX -*-
 % ... preamble ...
\documentclass[times,12pt,titlepage]{mstthesis}
\doublespacing
\usepackage{threeparttable}
\usepackage[final]{graphicx}
\usepackage{psfrag}
\usepackage{listings}
\usepackage{minted}
\usepackage[noprefix]{nomencl}
\usepackage{subcaption}
\usepackage{xr}
\usepackage{rotating}
\makenomenclature
\renewcommand{\nomgroup}[1]{
   \ifthenelse{\equal{#1}{A}}{\medskip \item \textbf{Roman}}{}%
   \ifthenelse{\equal{#1}{G}}{\medskip \item \textbf{Greek}}{}%
   \ifthenelse{\equal{#1}{S}}{\medskip \item \textbf{Subscripts}}{}%
}
\usepackage[nopar]{lipsum} % ... provides dummy text ...

@@

\begin{Vita}
Edward Norris graduated from Missouri University of Science and Technology in 2013 with a B.S. in both nuclear engineering and computer science, he is currently pursuing both a M.S. in computer science and a PhD in nuclear engineering. His PhD work is currently funded by a fellowship through the NRC.

Previously he has participated in four summer internships at Sandia National Laboratories. While there, he served in various capacities ranging from cyber defense to radiation detection and neutron scatter simulation. He was largely involved with numerical simulations of radiation transport using Geant4 and MCNP6 as well as data collection.

Edward was awarded the College of Engineering and Computing PhD Scholar award in 2017 for his academic achievements.

@@

After completing his PhD, he plans to take a one year postdoctorial fellowship position with the NNSA.
